\documentclass[letter]{res}

\batchmode

\setlength{\textheight}{9.5in}
%\usepackage{fontspec}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\geometry{
 a4paper,
 total={210mm,297mm},
 left=20mm,
 right=25mm,
 top=17mm,
 bottom=17mm,
 bindingoffset=0mm
 }\usepackage{fontenc}
\usepackage{enumitem}
\setlist{nolistsep}
%\usepackage[colorinlistoftodos]{todonotes}
%\setmainfont[Mapping=tex-text]{Linux Libertine O}


\begin{document}

\name{\huge Vivek Rai \\[14pt]}
\address{ \texttt{\href{mailto:vivekrai@iitkgp.ac.in}{vivekrai@iitkgp.ac.in} }}
\address{
  \texttt{\url{vivekiitkgp.github.io} }} 
\begin{resume}
  \noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}

\section{Education}
\vspace{1mm}
{\sl B.Tech \& M.Tech (Integrated)} - Biotechnology (8.65/10)\hfill May 2017\\
\href{http://iitkgp.ac.in}{Indian Institute of Technology Kharagpur}, India

\section{Research Experience}
\vspace{1mm}
\href{http://systemsbiology.org/}{Institute for Systems Biology} | Seattle, WA \newline
 {\sl \href{https://www.systemsbiology.org/bio/gustavo-glusman-phd/}{Dr. Gustavo Glusman}, Research Intern} \hfill May 2016 – July 2016\\
 \vspace{-2mm}
 \begin{itemize}
  \item Analyzed sex-specific technological biases in the whole-genome sequencing pipelines.
 \end{itemize}
  \vspace{-2mm}

\href{http://www.iisc.ernet.in/}{Indian Institute of Science} | Bangalore, India \newline
{\sl \href{http://mrdg.iisc.ernet.in/sandhyav/index.htm}{Prof. Sandhya M. Visweswariah}, Research Intern} \hfill May 2015 – July 2015\\
  \vspace{-2mm}
  \begin{itemize}
    \item Fluorescent labeling and lipid phase dependence \href{https://vivekiitkgp.github.io/science/intern-at-iisc-2.html}{study} of E.coli ClyA pore-forming protein.
  \end{itemize}
  \vspace{-2mm}

\section{Development Experience}
\vspace{1mm}

 \href{https://summerofcode.withgoogle.com}{Google Summer of Code} | Google Inc., \newline
 {\sl \href{https://summerofcode.withgoogle.com/organizations/5693436329984000/#4637393399316480}{openSNP (OBF)}, Developer}\hfill  May 2016 – Aug 2016\\
  \vspace{-2mm}
 \begin{itemize}
  \item Developed algorithm to link the Phenotypes with Genotypes (SNPs) in OpenSNP portal.
  \item Implemented database models and visualizations to view the linkage information.
 \end{itemize}
  \vspace{-2mm}

 \href{https://meta.wikimedia.org/wiki/Grants:IEG/WIGI:_Wikipedia_Gender_Index}{Individual Engagement Grant} | Wikimedia Foundation \newline
 {\sl \href{http://whgi.wmflab.org}{WHGI}, Developer}\hfill Apr 2015 – Jan 2016\\
 \vspace{-2mm}
 \begin{itemize}
  \item Analyzed Wikidata to visualize gender bias across categories, performed statistical analysis.
  \item Developed the WHGI portal, coauthored paper, contributed to research and community efforts.
 \end{itemize}
 \vspace{-2mm}

 \href{http://wurmlab.github.io/}{Wurm Lab} | Queen Mary University of London \newline
 {\sl \href{http://sequenceserver.com}{Sequeneserver}, Developer}\hfill Apr 2014 – Jan 2016\\
 \vspace{-2mm}
 \begin{itemize}
  \item Developed backend data and output parser module in Ruby, designed
  graphical overview scheme.
  \item Contributed more than 110 commits over an year and co-authored the research paper.
 \end{itemize}
 \vspace{-2mm}

\section{Skills}
{\sl Programming Languages:}  Python, R, BASH (shell sripting), SQL, JavaScript \\
{\sl Operating Systems:} Linux/Unix \\
{\sl Software:} Git, Vim, \LaTeX, CLI
\vspace{-2mm}

\section{Coferences and Publications}
\begin{itemize}
  \item Priyam, Woodcraft, {\bf Rai} \textit{et al.}, ``Sequenceserver: a modern graphical user interface for custom BLAST databases.'' \url{http://sequenceserver.com} | \href{http://www.biorxiv.org/content/early/2015/11/27/033142}{Bioarxiv}
  \item Klein, Gupta, {\bf Rai} \textit{et al.}, ``Monitoring the Gender Gap with Wikidata Human Gender Indicators'' | \href{http://whgi.wmflabs.org/monitoring-gender-gap.pdf}{OpenSym, 2016}
  \item Winter School | \href{https://www.icts.res.in/program/current/details/361/}{Quantitative Systems Biology}, 2016
\end{itemize}
\vspace{-2mm}

\section{Activities} 
\begin{itemize}
\item \href{http://2015.igem.org/Team:IIT_Kharagpur}{iGEM, IIT Kharagpur} | Wet lab, Core Team Member
\item \href{http://wiki.metakgp.org}{metaKGP}, Open Wiki and community  | Administrator (Present)
\item \href{https://www.hackerrank.com}{Hackerrank}, Ruby Programming Language | Problem Setter
 \end{itemize}
\vspace{-2mm}
 
\section{Awards} 
\begin{itemize}
  \item Awarded first prize in Wikidata competition 2016 organized by \href{http://iscb.org/}{ISCB}.
  \item Awarded third prize in Wikipedia competition 2016 organized by ISCB.
  \item Awarded Department of Biotechnology - GATE scholarship in 2016-17.
  \item Awarded tution scholarship throughout 2012-2016.
\end{itemize}
\vspace{-2mm}

\end{resume}
\end{document}



